\PaperTitle

### 2024-05-05 Final_Report/paper.tex
protocol

Consequently, the features selected for training and testing the models are Time, Length, and Protocol. The Protocol feature is converted to an integer for compatibility with 
the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., \texttt{TCP}: 0, \texttt{QUIC}: 1, \texttt{TLSv1.2}: 2) as shown in Figure \ref{fig:webTraffic}.  Additionally, a categorical variable titled "Website" 
is created which displays which website the packet originated (e.g., LinkedIn, ChatGPT, Blackboard). The "Website" feature acts as the target variable and allows 
the models to detect relationships between the packets and their corresponding web traffic origin.

@@

First, as you can see from the Actual sample space scatter plot, there is a lot of clustering of the data, particularly in terms of the Protocol feature. ChatGPT uses almost exclusively QUIC protocols, whereas Blackboard and LinkedIn use a mix of TCP and TLSv1.2. This makes differentiating ChatGPT from either of the others trivially easy, but disambiguating Blackboard and LinkedIn relatively hard.

@@

Since Protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length. In Figure \ref{fig:time_scatter}, see that Blackboard has significantly lower time values that LinkedIn. 
This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per Figure \ref{fig:length_scatter}.

>>>>

Consequently, the features selected for training and testing the models are time, length, and protocol. The protocol feature is converted to an integer for compatibility with 
the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., \texttt{TCP}: 0, \texttt{QUIC}: 1, \texttt{TLSv1.2}: 2) as shown in Figure \ref{fig:webTraffic}.  Additionally, a categorical variable titled "Website" 
is created which displays which website the packet originated (e.g., LinkedIn, ChatGPT, Blackboard). The "Website" feature acts as the target variable and allows 
the models to detect relationships between the packets and their corresponding web traffic origin.

@@

First, as you can see from the Actual sample space scatter plot, there is a lot of clustering of the data, particularly in terms of the protocol feature. ChatGPT uses almost exclusively QUIC protocols, whereas Blackboard and LinkedIn use a mix of TCP and TLSv1.2. This makes differentiating ChatGPT from either of the others trivially easy, but disambiguating Blackboard and LinkedIn relatively hard.

@@

Since protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length. In Figure \ref{fig:time_scatter}, see that Blackboard has significantly lower time values that LinkedIn. 
This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per Figure \ref{fig:length_scatter}.
